\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-16 paper/figures.tex
add latency figure to paper and explain

>>>>

\newcommand{\FigLatency}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/td-dd-latency.pdf}
    \caption{\textbf{Latency}\,---\, %
        We compare the CDF of latency for requests between \scheme and TapDance.
        In each case, we have a long-lived session over which requests are being made
        using Apache Benchmark (ab). At the median, \scheme has 44~ms (19\%) faster latency than
        TapDance.
        In addition, TapDance requests are frequently slowed by its intermittent reconnections
        to the decoy, as shown in the longer tail of TapDance's latency CDF. \scheme has no such
        reconnects, and thus has more uniform latency. At the 99th
        percentile, \scheme is 281~ms (92\%) faster than TapDance.
    }
    \label{fig:latency}
\end{figure}
}

### 2019-05-16 paper/paper.tex
add latency figure to paper and explain

To evaluate our \scheme implementation, we compare its bandwidth
to that of TapDance in a realistic ISP setting. We used a 20~Gbps
network tap at a mid-sized ISP and run both implementations on a 1U server with
an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
network interface. A typical week of bandwidth seen on the tap is
shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
17~Gbps.

We evaluated the performance of a client from a Singapore-based VPS,
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
measured by iperf for TapDance, our \scheme implementation, and a direct
connection to our iperf server in the ISP's network.

@@

>>>>

To evaluate our \scheme implementation, we compare its bandwidth and latency
to that of TapDance in a realistic ISP setting. We used a 20~Gbps
network tap at a mid-sized ISP and run both implementations on a 1U server with
an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
network interface. A typical week of bandwidth seen on the tap is
shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
17~Gbps.

We evaluated the performance of a client from an India-based VPS,
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
measured by iperf for TapDance, our \scheme implementation, and a direct
connection to our iperf server in the ISP's network.

@@

We also measure the latency of repeated small requests. In both \scheme (using
the OSSH protocol) and
TapDance we establish a single session tunnel using our integrated Psiphon
client, and make 1000 requests through each using Apache Benchmark (ab). We find
that our India-based VPS throttles TLS but not OSSH, making TapDance twice as slow as
\scheme. We repeated these tests on a US-based VPS which does not have such
throttling, and show results in Figure~\ref{fig:latency}. TapDance's frequent
reconnects adds significant latency to about 10\% of requests. In addition, the
median latency of \scheme is about 19\% faster, due to the added
overhead of TLS and the complex path that TapDance data packets take through
the station compared to \scheme.

\FigLatency
